Quantifying the home ground advantage

### 2019-12-25 inst/home_advantage.Rmd
slight tweaks

```{r}
small <- 1e-4
f <- function(home_strength){
  maxp(H,startp=rep((1-small)/4,4),give=TRUE,fcm=t(rep(1,4)),fcv=1-home_strength)$value
}
```

See how the ```fcm``` and ```fcv``` constraints make the sum of
a,b,c,d, greater than 1-home_strength.  Thus 'home' [which is the
fillup value] is constrained to be less than home_strength.  Using
this function, the likelihood ratio test is straightforward:

```{r}
Lambda <- -2*(f(2e-4)-maxp(H,give=TRUE)$value)
Lambda
```

Under the null, Wilks's theorem gives us that Lambda is distributed as
a chi-square with 1 degree of freedom (clearly rejected).  However, it
is always interesting to plot likelihood functions.To plot a profile
likelihood we can constrain the home to be greater than a particular
value:

```{r}
g <- function(home_strength){
  maxp(H,startp=rep(small/4,4),give=TRUE,fcm=-t(rep(1,4)),fcv=home_strength-1)$value
}
```

>>>>

```{r}
f <- function(home){
	small <- 1e-3
	maxp(H,startp=rep((1-small)/4,4),give=TRUE,fcm=t(rep(1,4)),fcv=1-home)$value
}
```

See how the ```fcm``` and ```fcv``` constraints make the sum of
a,b,c,d, greater than ```1-home```.  Thus 'home' [which is the fillup
value, $p_\mathrm<{home}=1-(p_A+p_B+p_C+p_D)$] is constrained to be
less than argument ```home```.  Using this function, the likelihood
ratio test is straightforward:

```{r}
Lambda <- -2*(f(0.01)-maxp(H,give=TRUE)$value)
Lambda
```

Under the null, Wilks's theorem gives us that Lambda is distributed as
a chi-square with 1 degree of freedom (clearly rejected).  However, it
is always interesting to plot likelihood functions.  To plot a profile
likelihood we can constrain the home to be greater than a particular
value:

```{r}
g <- function(home){
	small <- 1e-3
	maxp(H,startp=rep(small/4,4),give=TRUE,fcm=-t(rep(1,4)),fcv=home-1)$value
}
```
